---
title: "QMM Assignment"
author: "Bhargav"
date: "2023-09-19"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
#Defining the Decision variables:
##Decision variables for 3 plants
  A1= Quantity of products produced by Plant1 of size large
  B1= Quantity of products produced by Plant1 of size medium
  C1= Quantity of products produced by Plant1 of size small
  A2= Quantity of products produced by Plant2 of size large
  B2= Quantity of products produced by Plant2 of size medium
  C2= Quantity of products produced by Plant2 of size small
  A3= Quantity of products produced by Plant3 of size large
  B3= Quantity of products produced by Plant3 of size medium
  C3= Quantity of products produced by Plant3 of size small


#further we need to specify objective function, constraints, direction, right hand side(constants) to solve the problem.

##Objective Function:
  The objective function to maximize the profit. So,
  max z= 420 * (A1+A2+A3) +360*(B1+B2+B3) +300*(C1+C2+C3)
  That can be written as,
  max z= 420A1 +360B1 +300C1 +420A2 +360B2 +300C2 +420A3 +360B3 +300C3

##Constraints:
  A1 +B1 +C1 <=750
  A2 +B2 +C2 <=900
  A3 +B3 +C3 <=450
  20A1 +15B1 +12C1 <= 13000
  20A2 +15B2 +12C2 <= 12000
  20A3 +15B3 +12C3 <= 5000
  A1 +A2 +A3 <= 900
  B1 +B2 +B3 <= 1200
  C1 +C2 +C3 <= 750
  (A1 +B1 +C1)/ 750 = (A2 +B2 +C2)/ 900 = (A3 +B3 +C3)/ 450
  
Non Negativity Constraints,
  A1, A2, A3, B1, B2, B3, C1, C2, C3 >= 0

The above constraints can be written as,
  A1 +B1 +C1 +0*A2 +0*B2 +0*C2 +0*A3 +0*B3 +0*C3 <=750
  0*A1 +0*B1 +0*C1 +A2 +B2 +C2 +0*A3 +0*B3 +0*C3 <=900
  0*A1 +0*B1 +0*C1 +0*A2 +0*B2 +0*C2 +A3 +B3 +C3 <=450
  20A1 +15B1 +12C1 +0*A2 +0*B2 +0*C2 +0*A3 +0*B3 +0*C3 <= 13000
  0*A1 +0*B1 +0*C1 +20A2 +15B2 +12C2 +0*A3 +0*B3 +0*C3 <= 12000
  0*A1 +0*B1 +0*C1 +0*A2 +0*B2 +0*C2 +20A3 +15B3 +12C3 <= 5000
  A1 +0*B1 +0*C1 +A2 +0*B2 +0*C2 +A3 +0*B3 +0*C3 <= 900
  0*A1 +B1 +0*C1 +0*A2 +B2 +0*C2 +0*A3 +B3 +0*C3 <= 1200
  0*A1 +0*B1 +C1 +0*A2 +0*B2 +C2 +0*A3 +0*B3 +C3 <= 750
  900*A1 +900*B1 +900*C1 -750*A2 -750*B2 -750*C2 +0*A3 +0*B3 +0*C3 =0
  0*A1 +0*B1 +0*C1 +450*A2 +450*B2 +450*C2 -900*A3 -900*B3 -900*C3 =0
  450*A1 +450*B1 +450*C1 +0*A2 +0*B2 +0*C2 -900*A3 -900*B3 -900*C3 =0


```{r}
#Calling the 'lpSolve' library and declaring the objective function as 'f.obj'
#library
library(lpSolve)

#objective function
f.obj <- c(420,360,300,420,360,300,420,360,300)

#Declaring the constraints as 'f.con'
f.con <- matrix(c( 1, 1, 1, 0, 0, 0, 0, 0, 0,
                   0, 0, 0, 1, 1, 1, 0, 0, 0,
                   0, 0, 0, 0, 0, 0, 1, 1, 1,
                   20, 15, 12, 0, 0, 0, 0, 0, 0,
                   0, 0, 0, 20, 15, 12, 0, 0, 0,
                   0, 0, 0, 0, 0, 0, 20, 15, 12,
                   1, 0, 0, 1, 0, 0, 1, 0, 0,
                   0, 1, 0, 0, 1, 0, 0, 1, 0,
                   0, 0, 1, 0, 0, 1, 0, 0, 1,
                   900, 900, 900, -750, -750, -750, 0, 0, 0,
                   0, 0, 0, 450, 450, 450, -900, -900, -900,
                   450, 450, 450, 0, 0, 0, -750, -750, -750),ncol = 9, byrow=TRUE)

#Declaring the directions as 'f.dir'
f.dir <- c("<=",
           "<=",
           "<=",
           "<=",
           "<=",
           "<=",
           "<=",
           "<=",
           "<=",
           "=",
           "=",
           "=")

#Declaring the Right hand side constants as 'f.rhs'
f.rhs <- c(750, 900, 450, 13000, 12000, 5000, 900, 1200, 750, 0, 0, 0)

```
```{r}
#Calling the LP function to Solve the problem based on objective function to maximize the profit
f.max <- lp("max", f.obj, f.con, f.dir, f.rhs)
f.max

#Calling the LP function to get the values for Variables defined above
f.max$solution
```
```{r}
#Calling the LP function to Solve the problem based on objective function to maximize the profit using 'int.vec'
f.max2 <- lp("max", f.obj, f.con, f.dir, f.rhs, int.vec=1:9) #int.vec to get exact values                                                                of variables
f.max2

#Calling the LP function to get the values for Variables defined above, with int.vec
f.max2$solution
```


